Cooling Requirements for the Vertical Shear Instability in Protoplanetary Disks

### 2015-05-07 application.tex
mkl edits of 5.3, 6.0, 6.1, 7; atlanta file updates

\begin{figure}
  \includegraphics[width=\linewidth]{figures/bcrit_mink} 
  \caption{The minimum perturbation wavenumber $\khat$ in
    the MMSN such that the associated dimensionless thermal
    relaxation time $\beta$ at $z=0$ (solid) and $z=3H$ (dashed) is
    less than the critical timescale $\beta_\mathrm{crit}$.   
    \label{mmsn_bcrit_bcool_mink}}   
\end{figure}

Fig. \ref{mmsn_bcrit_bcool_mink} highlights this wavenumber dependence by plotting
the wavenumbers for which $\beta = \beta_\mathrm{crit}$.  Above the solid curves (i.e.\ for larger wavenumbers), $\beta <  \beta_\mathrm{crit}$ at all disk heights, implying linear VSI growth.  Below the dashed curves, VSI growth is strongly suppressed since $\beta >  \beta_\mathrm{crit}$ for all $|z| > 3H$.  Between the solid and dashed curves some growth is possible, but only fairly close to the solid curve (according to \S\ref{vsi_mmsn_grow}).  Thus linear growth of the VSI near 1 AU is only possible if $k_x \gtrsim 10^3/H$.  As argued elsewhere, we doubt that such small-scale disturbances will drive significant turbulence or transport.

@@

\emph{Big question, do we need to include disk mass as another parameter to vary.  Or not in this study.  Has been included in SK14.}

@@

Fig. \ref{mmsn_overall} shows that in the MMSN, the VSI  is active from $r_\mathrm{AU}\sim 5$ to $r_\mathrm{AU}\sim
50$ with growth timescales $\sim 30$---40 orbits.  A small radius cufoff exists, inside of which growth is strongly suppressed.  The cutoff occurs at smaller radii for larger wavenumbers, as expected from Fig.\ \ref{mmsn_bcrit_bcool_mink}.  Growth at smaller disk radii is possible for yet larger wavenumbers, yet we remain skeptical about the non-linear viability of such short modes.

The growth times rise gradually as $r$ increases towards 100 AU in Fig. \ref{mmsn_overall}.  This trend is expected as the outer radius cutoff at $\sim 200$AU (from Fig.\ \ref{mmsn_bcrit_bcool}) is approached.

@@

\emph{I don't understand the specific comparison being made here, especially since N13 is for vert.\ constant beta.  Maybe remind me of which specific result/figure.  I would think the more relevant comparison is to SK14 (either here or in discussion).}
 Our numerical results suggest the VSI
is efficient at radii of few tens of AU in the MMSN, consistent with
estimates made by \citetalias{nelson13}.

>>>>

\begin{figure}
  \includegraphics[width=\linewidth]{figures/bcrit_mink} 
  \caption{The minimum perturbation wavenumber $\khat$ in
    the MMSN such that the associated dimensionless thermal
    relaxation time $\beta$ at $z=0$ (solid) and $z=3H$ (dashed) is
    less than the critical timescale $\beta_\mathrm{crit}$. Asterisks
    correspond to the inner cut-off radii shown in
    Fig. \ref{mmsn_overall}.   
    \label{mmsn_bcrit_bcool_mink}}   
\end{figure}

Fig. \ref{mmsn_bcrit_bcool_mink} highlights this wavenumber dependence by plotting
the wavenumbers for which $\beta = \beta_\mathrm{crit}$.  Above the
solid curves (i.e.\ for larger wavenumbers), $\beta <
\beta_\mathrm{crit}$ at all disk heights, implying linear VSI growth.
Below the dashed curves, VSI growth is strongly suppressed since
$\beta >  \beta_\mathrm{crit}$ for all $|z| < 3H$.  Between the solid
and dashed curves some growth is possible, but only fairly close to
the solid curve (according to \S\ref{vsi_mmsn_grow}).  Thus linear
growth of the VSI near 1 AU is only possible if $k_x \gtrsim 10^3/H$.
As argued elsewhere, such small-scale disturbances may not 
drive significant turbulence or transport.

@@

% \emph{Big question, do we need to include disk mass as another parameter to vary.  Or not in this study.  Has been included in SK14.}

@@

Fig. \ref{mmsn_overall} shows that in the MMSN, the VSI  is active
from $r_\mathrm{AU}\sim 5$ to $r_\mathrm{AU}\sim 
50$ with growth timescales $\sim 30$---40 orbits.  A small radius
cut-off exists, inside of which growth is strongly suppressed.  The 
cut-off occurs at smaller radii for larger wavenumbers, as expected
from Fig.\ \ref{mmsn_bcrit_bcool_mink}.  Growth at smaller disk radii
is possible for yet larger wavenumbers, yet we remain skeptical about
the non-linear viability of such short modes.

The growth times rise gradually as $r$ increases towards 100AU in
Fig. \ref{mmsn_overall}.  This trend is expected as the outer radius
cutoff at $\sim 150$AU (from Fig.\ \ref{mmsn_bcrit_bcool}) is
approached. Our numerical results suggest the VSI is efficient at
radii of few tens of AU in the MMSN, consistent with estimates made by
\citetalias{nelson13} using the same disk model.

@@

% \emph{I don't understand the specific comparison being made here, especially since N13 is for vert.\ constant beta.  Maybe remind me of which specific result/figure.  I would think the more relevant comparison is to SK14 (either here or in discussion).}
